---
title: "p8105_hw5_ECW2178"
output: github_document
date: "2025-11-13"
---

```{r libraries_datasets}
library(tidyverse)
library(rvest)
```

```{r problem_1}
set.seed(343215)

bday_sim = function(n_room){
  birthdays = sample(1:365, n_room, replace = TRUE)
  repeated_bday = length(unique(birthdays)) < n_room
  repeated_bday
}

bday_sim(20)

bday_sim_results = 
  expand_grid(
    bdays = 2:50,
    iter = 1:10000
  ) %>% 
  mutate(
    result = map_lgl(bdays, bday_sim)
  ) %>% 
  group_by(bdays) %>% 
  summarize(
    prob_repeat = mean(result)
  )

bday_sim_results %>% 
  ggplot(aes(x = bdays, y = prob_repeat)) +
  geom_point() + 
  geom_line()
```

As expected, as the number in each group increases, there is a gradual increase in the probability of a repeated birthday. However, this increase is unexpectedly large- once there is more than 22 people in a group, there is a greater than 50% chance of a repeated birthday. 

```{r problem_2}
mu_list = c(0, 1, 2, 3, 4, 5, 6) 

dataset_generator = function(mu){
  n = 30
  sigma = 5
  
  sample = rnorm(n, mu, sigma)
  result = t.test(sample, mu = 0) %>% 
    broom::tidy()
  
  return(list(
    estimate = result$estimate,
    pvalue = result$p.value))
}

run_many = function(mu){
  out = vector("list", 5000)
  for (i in 1:5000){
    out [[i]] = dataset_generator(mu)
  }
  return(out)
}

all_results = vector("list", length(mu_list))

for (i in 1:length(mu_list)){
  all_results[[i]] = run_many(mu_list[i])
}


power_results = data.frame(estimate = numeric(),
                         pvalue = numeric(),
                         true_mu = numeric())

for (i in 1:length(mu_list)) {
  
  mu_value = mu_list[i]
  sims = all_results[[i]]  
  
  for (j in 1:length(sims)) {
    power_results = rbind(power_results,
                        data.frame(
                          estimate = sims[[j]]$estimate,
                          pvalue = sims[[j]]$pvalue,
                          true_mu = mu_value
                        ))
  }
}

power_example =  power_results %>%
  group_by(true_mu) %>%
  summarize(power = mean(pvalue < 0.05))

ggplot(power_example, aes(x = true_mu, y = power)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Power Curve for One-Sample t-test",
    x = "True Mean",
    y = "Power"
  )

average_estimates = power_results %>%
  group_by(true_mu) %>%
  summarize(avg_estimate = mean(estimate))

average_rejections = power_results %>%
  filter(pvalue < 0.05) %>%
  group_by(true_mu) %>%
  summarize(avg_estimate_rejected = mean(estimate))
  
ggplot(average_estimates, aes(x = mu, y = avg_estimate)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Average Estimate of mu Across Simulations",
    x = "True Mean",
    y = "Average mu hat"
  )

ggplot() +
  geom_line(data = average_estimates, aes(x = mu, y = avg_estimate)) +
  geom_point(data = average_estimates, aes(x = mu, y = avg_estimate)) +
  
  geom_line(data = average_rejections, aes(x = mu, y = avg_estimate_rejected), linetype = "dashed") +
  geom_point(data = average_rejections, aes(x = mu, y = avg_estimate_rejected)) +
  labs(
    title = "Average mu hat Overall vs. Conditional on Rejecting Null",
    x = "True Mean",
    y = "Average mu"
  )
```


The homicides raw dataset contains details of the arrests on individuals made across cities in the United States such as arrest ID, date of arrest, name, demographics, city, exact location, and disposition. 

```{r problem_3}
homicides_raw = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") 

homicides = homicides_raw %>% 
  mutate(city_state = paste(city, state, sep = ", ")) %>% 
  group_by(city_state) %>% 
  summarize(
    homicides = n(),
    unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  )

baltimore_homicides = homicides %>%
  filter(city_state == "Baltimore, MD")

baltimore_result = prop.test(baltimore_homicides$unsolved , baltimore_homicides$homicides) %>% 
    broom::tidy() %>%
    select(estimate, conf.low, conf.high)


city_results = homicides %>% 
  mutate(
    test = map2(unsolved, homicides, ~ prop.test(.x, .y)),
    tidy = map(test, broom::tidy)
  ) %>% 
  select(city_state, tidy) %>% 
  unnest(tidy) %>% 
  select(city_state, estimate, conf.low, conf.high)

city_results_plot = city_results %>% 
  arrange(estimate) %>% 
  mutate(city_state = factor(city_state, levels = city_state)) %>%  
  ggplot(aes(x = estimate, y = city_state)) +
  geom_point() +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = 0.2) +
  labs(
    x = "Proportion of Unsolved Homicides",
    y = "City",
    title = "Estimated Proportion of Unsolved Homicides by City"
  )
city_results_plot

```

